Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-14 paper.tex
Add spectra formulation; closes #58

Spectra of the cross-stream velocity normalized by the free stream are plotted
in Figure~\ref{fig:wake-spectra} for regions on either side of the turbine. On
the $-y$ side of the turbine there is broadband turbulence produced by blade
stall, and on the $+y$ side there is a clear peak in the spectra caused by the
blade passage. We see that on both sides there is higher spectral energy at
lower Reynolds numbers. On the $+y$ side of the turbine we notice higher
spectral energy at the blade passage frequency's first harmonic, or $6
f_\mathrm{turbine}$. This is likely due to the blade's shed vorticity being less
stable at higher $Re$.

@@

\caption{Cross-stream velocity (normalized by $U_\infty$) spectra at $z/H=0.25$,
    $y/R=-1.0$ ($-0.5$ m in Figure~\ref{fig:wake-locations}) (a) and $y/R=1.5$
    ($+0.75$ m in Figure~\ref{fig:wake-locations}) (b). Dashed vertical lines
    indicate $[1, 3, 6, 9]$ times the turbine rotational frequency.}

>>>>

Spectra of the cross-stream velocity normalized by the free stream were
computing using a fast Fourier transform-based method, applying a Hanning window
and averaging over four adjacent frequency bands to decrease confidence
intervals. These spectra are plotted in Figure~\ref{fig:wake-spectra} for
regions on either side of the turbine. On the $-y$ side of the turbine there is
broadband turbulence produced by blade stall, and on the $+y$ side there is a
clear peak in the spectra caused by the blade passage. We see that on both sides
there is higher spectral energy at lower Reynolds numbers. On the $+y$ side of
the turbine we notice higher spectral energy at the blade passage frequency's
first harmonic, or $6 f_\mathrm{turbine}$. This is likely due to the blade's
shed vorticity being less stable at higher $Re$.

@@

\caption{Cross-stream velocity (normalized by $U_\infty$) spectra at $z/H=0.25$,
    $y/R=-1.0$ ($-0.5$ m in Figure~\ref{fig:wake-locations}) (a) and $y/R=1.5$
    ($+0.75$ m in Figure~\ref{fig:wake-locations}) (b). Dashed vertical lines
    indicate $[1, 3, 6, 9]$ times the turbine rotational frequency. Shaded regions
    indicate 95\% confidence intervals assuming a $\chi^2$ distribution.}
